Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-11 paper.tex
Cite Sugar properly (?).
Switch to tighter "alternate" layout.  Much closer to our page budget now!
Add mechanism to suppress authors for review copy.
Properly cite Mark Riedl paper.
Tweak section; remove the Raven and use a flag rather than boots.

\section{A Lesson from Nell}
\begin{figure}
\centering
\epsfig{file=xo3-3.eps, width=3.2in}
\caption{Nell's solar-powered hardware platform.  The tablet design
  allows for direct interaction.}\label{fig:xo3}
\end{figure}
% tell a nell story up front
Miles from the nearest school, a young Ethiopian girl turns on a
tablet computer for the first time.  The solar-powered machine begins
talking to her immediately: \textit{``Hello!  Would you like to hear a story?''}

She nods and listens to a story about a princess.  Later, when
the girl has learned a little more, she will tell the machine that the
princess is named ``Rahel,'' like she is, and change all its
colors---but for now the green book draws pictures of the unnamed Princess
for her and asks her to trace shapes on the screen.

\textit{``R is for Raven.  Can you trace the R?''}

As she traces the R, it comes to life and gallops across the screen.
\textit{``Run starts with R.  Roger the R runs across the Red Rug.  Roger has a
dog named Rover.''}  Rover barks: \textit{``Ruff! Ruff!''}  The Princess asks,
\textit{``Can you find something Red?''} and Rahel uses the camera to
photograph her new boots.

@@

Automatic narrative generation has seen attention in
gaming, simulation, and training contexts~\cite{riedlXXX}.  Nell's
use of these ideas in a pedagogical context is unique.

>>>>

\section{A Lesson from Nell}
\begin{figure}
\centering
\epsfig{file=xo3-3.eps, width=3.2in}
\caption{Nell's solar-powered hardware platform.  The tablet design
  allows for direct interaction.}\label{fig:xo3}
\end{figure}
% tell a nell story up front
Miles from the nearest school, a young Ethiopian girl named Rahel turns on her
new tablet computer. The solar-powered machine greets her:
\textit{``Hello!  Would you like to hear a story?''}

She nods and listens to a story about a princess.  Later, when
the Rahel has learned a little more, she will tell the machine that the
princess is named ``Rahel'' like she is and she will change the princess'
colors---but for now the green book draws pictures of the unnamed Princess for
her and asks her to trace shapes on the screen.

\textit{``R is for Run.  Can you trace the R?''}

As she traces the R, it comes to life and gallops across the screen.
\textit{``Run starts with R.  Roger the R runs across the Red Rug.
Roger has a dog named Rover.''}  Rover barks: \textit{``Ruff! Ruff!''}  The
Princess asks, \textit{``Can you find something Red?''} and Rahel uses the
camera to photograph the red stripe on a nearby Ethiopian flag.

@@

Automatic narrative generation has seen attention in
gaming, simulation, and training contexts~\cite{riedl:2008}.  Nell's
use of these ideas in a pedagogical context is unique.
